\ \\ \LARGE\bf Rolling Horizon methods for Games with Continuous States and Actions

### 2014-04-08 lpaper/lunarcont.tex
More minor changes

Lunar Lander has a setup where a player gets rewards if and only if it actually lands on the pad. This creates the problem of rollouts (whether used by EVO-P or T-HOLOP) rarely will see a reward. In order to circumvent this, as it is common in other games, we use a heuristic for each state. Initially, we can define a number of vectors that portray the

@@

In the above Equation \ref{eq:h1} the constant C denotes the maximum magnitude of speed, which we set to $C=30$. $D = 60$ is the distance from the landing point $np$ where this heuristic takes precedence.  Intuitively, the upper part of the heuristic $h$ tries to get the ship above the landing point as fast as possible while maintaining a certain speed. The second part of the heuristic tries to minimise velocity on the $x$ axis (as the ship tries to land with maximum speed $C_l = 2$), maintain a minimum landing speed on the $y$ axis and get a certain angle (the summation term $f$) as close to vector $du$, i.e. help the ship stay upright through the duration of the rollout.  It's worth noting the main reason why we use a heuristic of this kind, one that includes not only the final state, but makes use of the path of the state as well, is that there is not enough information to discern states if one takes into account direction only, without incorporating the angular velocity. The ship might be spinning madly, but the end of the rollout might find it in the correct direction.

@@

For lunar lander, we do $10$ runs for each map in Figure \ref{fig:maps}, and the results for EVO-P can be seen in Table I. The results include the mean number of successful landings and the mean time it took to land the ship, alongside their confidence for the $95$th interval.   For EVO-P we used the default CMA-ES population size, each individual was bound between, each gene had a length of $8$ and each action pair ($x[i], x[i+1]$) was repeated $7$ times (where $x[i]$ represents thrust and $x[i+1]$ angular thrust). We derived these numbers experimentally and we did not optimise for them (not even implicitly) to any serious degree.

There are a number of things to notice here. The first one is that the only in Map D, where the ship starts the problem facing a wall do we get a failure to land, and this is due to a crash. This has to do with the fact that even a minor thrust can push you a bit forward and drive the ship to a position where there is no longer the possibility of recovery from a crush (or the combination of that recovery is extremely hard to get). The Second thing to observe is that we get there slowly, but this is by design, as we he have made the flying speed of the ship controllable. One can pottentially tweak all the default parameters we have used, plus the ones incorporated in CMA-ES as a kind of meta-heuristic search and achieve much better results. Another thing to note is that EVO-P lands the ship (on average) almost at the same time on MAPS B, C, D, although map has the same landscape as the other two but the ship is much closer. This is due to the fact that the minimum landing speed, set on one of our heuristics, is really low and The final thing we would like to note is that we have only included the results for EVO-P because T-HOLOP failed to land the ship using the same heuristic, and behaved badly. It's worth noting here that T-HOLOP requires rewards between certain bounds and this is not the case with our heuristic. For completeness purposes, we did change the UCB-like node selection policy of T-HOO to e-greedy, in which case we \emph{did} get the ship to behave reasonably, albeit the failure to land was evident here as well. This is important we think for a number of reasons. The first one is that it shows that different Heuristics might be needed for different algorithms. Although this might be self-evident, it shows that one must design heuristics with a specific algorithm in mind.

>>>>

Lunar Lander has a setup where an agent gets rewards if and only if she manages to land to actually land the ship on the pad. This creates the problem of rollouts (whether used by EVO-P or T-HOLOP) rarely will see a reward. In order to circumvent this, as it is common in other games, we use a heuristic for each state. Initially, we need define a number of vectors that portray ship directions:

@@

In the above Equation \ref{eq:h1} the constant C denotes the maximum magnitude of speed, which we set to $C=30$. $D = 60$ is the distance from the landing point $np$ where this heuristic takes precedence.  Intuitively, the upper part of the heuristic $h$ tries to get the ship above the landing point as fast as possible while maintaining a certain speed. The second part of the heuristic tries to minimise velocity on the $x$ axis (as the ship tries to land with maximum speed $C_l = 2$), maintain a minimum landing speed on the $y$ axis and get a certain angle (the summation term $f$) as close to vector $du$, i.e. help the ship stay upright through the duration of the rollout.  It's worth noting the main reason why we use a heuristic of this kind, one that includes not only the final state, but makes use of the path of the state as well, is that there is not enough information to discern states if one takes into account ship direction only; without incorporating the angular velocity. The ship might be spinning madly, but the end of the rollout might find it in the correct direction.

@@

For lunar lander, we do $10$ runs for each map in Figure \ref{fig:maps}, and the results for EVO-P can be seen in Table I. The results include the mean number of successful landings (\emph{Success Mean}) and the mean time it took to land the ship (\emph{Ticks Mean}), alongside their confidence for the $95$th interval.   For EVO-P we used the default CMA-ES population size, each individual was bound between, each gene had a length of $8$ and each action pair ($x[i], x[i+1]$) was repeated $7$ times (where $x[i]$ represents thrust and $x[i+1]$ angular thrust). We derived these numbers experimentally and we did not optimise for them (not even implicitly) to any serious degree.

There are a number of things to notice here. The first one is that the only in Map D, where the ship starts the problem facing a wall do we get a failure to land, and this is due to a crash. This has to do with the fact that even a minor thrust can push you a bit forward and drive the ship to a position where there is no longer the possibility of recovery from a crush (or the combination of that recovery is extremely hard to find). The second thing to observe is that we get there slowly, but this is by design, as we he have made the flying speed of the ship controllable. One can potentially tweak all the default parameters we have used, plus the ones incorporated in CMA-ES as a kind of meta-heuristic search and achieve much better results. Another thing to note is that EVO-P lands the ship (on average) almost at the same time on MAPS B, C, D, although map has the same landscape as the other two but the ship is much closer. This is due to the fact that the minimum landing speed, set on one of our heuristics, is really low. The final thing we would like to note is that we have only included the results for EVO-P because T-HOLOP failed to land the ship using the same heuristic, and behaved badly. It's worth noting here that T-HOLOP requires rewards between certain bounds, so they can be normalised around $[0,1]$ and this is not the case with our heuristic. For completeness purposes, we did change the UCB-like node selection policy of T-HOO to e-greedy, in which case we \emph{did} get the ship to behave reasonably, albeit the failure to land was evident here as well. This is important we think for a number of reasons. The first one is that it shows that different Heuristics might be needed for different algorithms. Although this might be self-evident, it shows that one must design heuristics with a specific algorithm in mind. The second is, but we can speculate at the time, that T-HOLOP spends too much trying to solve a hard problem than the one at hand. It will converge eventually, but the the Guassian approximation of CMA-ES seems to outperform it in the short term.
